Viscous Transport in Eroding Porous Media

### 2019-09-03 docs/transport/erosion_transport.tex
add two gap figures in section 4 of transport paper
add eight figures in section 6 of transport paper

The numerical methods to solve the governing fluid and erosion equations
are based on previous work of the authors~\cite{qua-moo2018}.  We
continue to use a boundary integral equation (BIE) formulation of the
incompressible Stokes equations and a second-order Runge-Kutta method
applied to a smoothed version of the magnitude of the shear stress.  In
our previous work, we discretized the BIE with the trapezoid rule whose
accuracy grows when evaluating layer potentials close to the fluid
boundary.  Therefore, given a fixed resolution, our previous work
required a minimum separation distance between all bodies to maintain
stability.  One of the earliest works on near-singular integration was
developed by Baker and Shelley~\cite{bak-she1986}, and in recent years,
many other near-singular integration schemes have been
developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
bea-lai2001, klo-bar-gre-one2013}.  In this work, we use a Barycentric
quadrature method~\cite{bar2014, bar-wu-vee2015} since it is a
non-intrusive modification of the trapezoid rule, and the error is
guaranteed to be uniformly bounded.  In this work, we extend this
quadrature method so that it can be used to compute the gradient of the
velocity which is required to compute the shear stress and the fluid
vorticity.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b400}
\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
bodies with the fixed pressure drop condition. The color is the
vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

@@

We plot the distribution of the gap sizes at four equally spaced points
in time in Figure~\ref{fig:Eroding100gap}.  At the initial configuration, there
are 100 bodies and 318 pairs of neighbors.  The mean distance between
these neighbors is $???  \times 10^{-???}$ and the variance is $???
\times 10^{???}$.  As the bodies erode, the mean and variance of the
distance between the bodies increases.  Finally, at the final time step,
there are only 82 bodies and 254 pairs of neighbors.
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The distribution of the gaps in the
case of erosion of 100 bodies at four time steps.}
\end{figure}

>>>>

The numerical methods to solve the governing fluid and erosion equations
are based on previous work of the authors~\cite{qua-moo2018}.  We
continue to use a boundary integral equation (BIE) formulation of the
incompressible Stokes equations and a second-order Runge-Kutta method
applied to a smoothed version of the magnitude of the shear stress.  In
our previous work, we discretized the BIE with the trapezoid rule whose
accuracy grows when evaluating layer potentials close to the fluid
boundary.  Therefore, given a fixed resolution, our previous work
required a minimum separation distance between all bodies to maintain
stability.  One of the earliest works on near-singular integration was
developed by Baker and Shelley~\cite{bak-she1986}, and in recent years,
many other near-singular integration schemes have been
developed~\cite{oja-tor2015, kli-tor2018, hel-oja2008a, bea-yin-wil2016,
bea-lai2001, klo-bar-gre-one2013}.  In this work, we use a Barycentric
quadrature method~\cite{bar2014, bar-wu-vee2015} since it is a
non-intrusive modification of the trapezoid rule, and the error is
guaranteed to be uniformly bounded.  In this work, we extend this
quadrature method so that it can be used to compute the gradient of the
velocity which is required to compute the shear stress and the fluid
vorticity. 
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b400}
\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
bodies with the fixed pressure drop condition. The color is the
vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height =0.8\linewidth]{./figs/triangulation_100b100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_hist100b100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap} (a): The Delaunay triangulation of the porous media. 
(b): The distribution of gaps from (a).}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var} (a): The mean of gaps with respect to porosity $\phi$.  
(b): The variance of gaps with respect to porosity $\phi$.}
\end{figure}

We plot the distribution of the gap sizes at six porosities
in Figure~\ref{fig:Eroding100gap_hist}.  At the initial configuration, there
are 100 bodies and 258 pairs of neighbors.  The mean distance between
these neighbors is $???  \times 10^{-???}$ and the variance is $???
\times 10^{???}$.  As the bodies erode, the mean and variance of the
distance between the bodies increases.  Finally, when the porosity reaches $95.12\%$
there are only 34 bodies and 74 pairs of neighbors.

\begin{figure}[H]
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_1}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_46}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_112}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_164}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_207}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics*[width =\linewidth]{./figs/hist100b_246}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_hist} The distribution of the gaps in the
case of erosion of 100 bodies at six porosities. (a) 100 bodies with 258 gaps as porosity $\phi = 50.09 \%$. 
(b) 100 bodies with 258 gaps as porosity $\phi = 55.02 \%$. 
(c) 97 bodies with 249 gaps as porosity $\phi = 65.03 \%$. 
(d) 92 bodies with 234 gaps as porosity $\phi = 75.14 \%$. 
(e) 75 bodies with 189 gaps as porosity $\phi = 85.07 \%$. 
(f)} 34 bodies with 74 gaps as porosity $\phi = 95.12 \%$. 
\end{figure}
